\vspace{24pt} In-Memory Trajectory Analysis on Taxi Data

### 2018-08-22 paper/paper.tex
started data cleansing part, set line endings ti \n

The data we used is a freely available collection of GPS information of taxis. \footnote{\href{https://www-users.cs.umn.edu/~tianhe/BIGDATA/UrbanCPS/TaxiData/TaxiData}{https://www-users.cs.umn.edu/$\sim$tianhe/BIGDATA/UrbanCPS/TaxiData/TaxiData}} The dataset set has been collected over one day starting at 12 AM and 23:59 PM in the city of Shenzhen, China and the surrounding area. The data does not only contain the GPS location at a certain time, but also the current speed and the taxi's occupancy. The status of a driving taxi has been recorded in an average interval of 26.85 seconds or every 15 seconds in median. In total there are 14,728 trajectories traced resulting in almost 47 million records. The data comes in CSV-format which can be loaded into the SAP HANA database immediately. The total memory consumption without any further optimization (e.g. indices) of the Shenzhen data takes 541 MB.

\subsection{Data Cleansing}

>>>>

The data we used is a freely available collection of GPS information of taxis.\footnote{\href{https://www-users.cs.umn.edu/~tianhe/BIGDATA/UrbanCPS/TaxiData/TaxiData}{https://www-users.cs.umn.edu/$\sim$tianhe/BIGDATA/UrbanCPS/TaxiData/TaxiData}} The dataset set has been collected over one day starting at 12 AM and 23:59 PM in the city of Shenzhen, China and the surrounding area. The data does not only contain the GPS location at a certain time, but also the current speed and the taxi's occupancy. The status of a driving taxi has been recorded in an average interval of 26.85 seconds or every 15 seconds in median. In total there are 14,728 trajectories traced resulting in almost 47 million records. The data comes in CSV-format which can be loaded into the SAP HANA database immediately. The total memory consumption without any further optimization (e.g. indices) of the Shenzhen data takes 541 MB.

\subsection{Data Cleansing}
Before we started analyzing the trajectories we had a closer look at the dataset itself. We noticed rather soon, that there are some inconsistencies within data. Hence, we perform data cleansing. In the following paragraphs, we describe our criteria for data cleansing in detail.

\subsubsection{Duplicates}
The data was already imported into the database by our supervisor, when we started our project. Since, we did not want to change the the original data we created an own table. Once we wanted to create a primary key, the database has thrown an error stating that the data has duplicate values. In fact, there are 381 data points occuring not only twice, but also multiple times. We deleted those entries, because they do not add any value to the data and prevent the creation of a primary key.

\subsubsection{Bounding box}
\subsubsection{Small trajectories}
\subsubsection{Wrong passenger status}
\subsubsection{Jumps}
\subsubsection{Summary: Data cleansing}
